### 2011-06-17 thesis/introduction.tex
Context on introduction done.

\section{Context}
% Spatial Semantics only!
% Mobile Robotics
% Room Categories

Being able to deal with any 
in this sense this thesis will focus only on the semantic spatial mapping problem.

Humans organize spaces as areas, they characterize them by the type of

% Yeah thats what you call dream :P
In an extreme ideal case the agent should be able to go from zero-knowledge to
understanding presence of certain objects (as generators of a set of sensed
sensed properties grouped locally), understand areas within rooms (sink-area on
on a kitchen), rooms as separated by doors, and understand environments such
as office, home, warehouse, spaceship.

% Semantic knowledge (spatial-knowledge)
% It also holds an important role in long-term planning and stability as it
% hides the space-time local details and allows to focus on high-level thinking.

In that sense the need for semantic mapping arises, and it can be described as the
relation between spatial areas and a set of existent concepts used by humans to
describe them.

, not just for the purpose of navigation and obstacle avoidance, 
but also in terms of human semantics and functionality.

An essential competence for cognitives robots is their ability to reason about space.
Spatial knowledge plays an important role in navigation, reasoning, planning and episodic memory.
% == Introduce the need of semantic representations ==
%
% There is a lot of low-level methods (or specific knowledge to robots)
% But the creation of semantic representations allow to bridge that low-level
% sensing with high-level concepts that facilitate several high-level Tasks.

% Spatial knowledge representation
% Semantic Mapping

@@

>>>>

\section{Context}
% Spatial Representations
% Spatial Semantics only!
% Room Categories actually.

%
In mobile robotics the main need is on spatial information. Having a representation of all
the spatial entities and relations between them allow the robot to navigate and interact
with them. Maps are the default tool for representing those spaces, and computers excel at
creating close to exact representations of spatial environments.
But which concepts existent in the human spatial knowledge are needed in order to turn those
representations a usable tool to represent human concepts?

Different spatial knowledge types can be identified depending on the scale, abstraction level,
and required generalization. For example geometric type aspects which robots are already very
good at representing, object knowledge which is incredibly basic for humans, delineation
of spatial areas and relations between instances of all those knowledge types. e.g.\ a specific
object (book) is on top of another object (table) that is located inside an area (room-library)
that is inside a another area (university).
As seen on this example humans do not limit themselves at representing entities
in space and spatially relate them but they also attribute semantic value to them.

It is this semantic value attributed by humans to entities that is interesting for endowing
robots with knowledge on how to interpret and reason over human environments.
By understanding which objects are expected to be found on a room, what are the properties that
distinguish room categories, which room types are likely to be connected together a robot can
aim at increase its effectiveness on indoor environments.

A basic concept on indoor environments is that of room. Rooms allow humans to segment areas
in high\hyp{}level entities that can be categorized according to the properties and expected
activities to be performed on them.
e.g.\ kitchens are rooms where cornflakes are usually found, a library is identified by the presence
of many books, a lecture hall is a place where lessons are given.
Since room categories play an important role in understanding and reasoning about
indoor human environments this thesis will focus on them.

@@

Being able to represent all this type of knowledge is an huge task on itself and this thesis
focus mainly on how to detect novelty on semantic values  
Pronobis~\cite{pronobis2011phd} has tackled this problem by proposing
